Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-07 ms_pre_post.Rmd
Mid-sentence edit in the last paragraph, but it's time to go home

Another general inference from our simulation results concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits. The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001]. Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics. In the context of reproductive strategy, pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability. Hence, degeneracy occurred in our model through an overlap in how phenotypes cause adaptive inbreeding avoidance. Such degeneracy might increase biological robustness [@Gardner2006; @Whitacre2010a], potentially facilitating realised inbreeding avoidance across environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation). However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997]. The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.

>>>>

<!--- By removing the sentence specifying how degeneracy works with respect to inbreeding avoidance, we are asking the readers to recall these specifics from the introduction (or go back and find them again). The exact mechanism by which functional overlap occurs is removed from the more vague 'phenotypic reproductive strategies'. I'm afraid this will lose some readers who might be a bit tired by the end of the Discussion.--->

Degeneracy occurs at nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009], community [@Suraci2017], and ecosystem [e.g., @Levin2008] dynamics. In our model, degeneracy occurred through overlaps in how different reproductive strategies caused adaptive inbreeding avoidance. In general, degeneracy might increase biological robustness by fine-tuning degenerate phenotypes to different local environments [@Gardner2006; @Whitacre2010a]. For example, such degeneracy might facilitate inbreeding avoidance via pre-copulatory or post-copulatory mechanisms depending on different selective environments in which either pre-copulatory or post-copulatory mechanisms alone would be ineffective (e.g., due to sexual conflict affecting mate choice or injury affecting fertilisation). However, evolution of each of these strategies might decrease selection on the other strategy by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression [*sensu* evolution of genetic redundancy; see @Nowak1997]. The relevance of degeneracy with respect to such reproductive strategies therefore requires further theoretical development, which could result in new empirical predictions and conceptual synthesis across biological scales.
